---
output: 
  html_document: 
    keep_md: yes
---
s---
title: "Homework 1--Data frame exploration"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data frame exploration

THe dataset used in this homework is a spread-sheet obtain online. It contains data from which conclusions  that were  drawn  in  the  article  "Sleep  in 
Mammals: Ecological and Constitutional Correlates" by Allison, T.  and 
Cicchetti, D. (1976), _Science_, November 12, vol. 194,  pp.  732-734. 

Some rows that contain missing values and some columns were removed from the data, and it was saved as mammals.csv file.

### Setting up
First, to import the .csv file into R.

```{r}
data.file = "mammals.csv"
dat = read.csv(data.file, header = TRUE)
```


### Exploration of data frame

A few funtions as `head`, `ncol`, `str`, and `summary` will be shown as follows.

```{r}
head(dat)
ncol(dat)
str(dat)
summary(dat)
```

### Extracting columns and making some plots

First, let's extract some columns
```{r}
predation_index = dat$PredationIndex
danger_index = dat$OverallDanger
```

Plot a dot plot that has two variables that are body weight and life span
```{r}
plot(danger_index, predation_index)
```


